Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Responding to comments

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}
The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes
\raft{Not a characterization!}
the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.

@@

\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{report space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate report with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the report space for every outcome $y \in \Y$.

Because the paper focuses heavily on conditional distributions over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
The probability simplex over $\Y$ is $\simplex$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
For a distribution $p \in \simplex$, we denote the expected target loss for report $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
We call the excess loss over the optimal the \emph{regret} of a loss $L(u; p)$; that is, $R_L(u,p) := L(u;p) - \inf_{u^*} L(u^*; p)$.

@@

\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We want to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.}
Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}
For discrete prediction problems, one often starts with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
However, starting with an (often discrete) target loss is often a computationally hard problem.
For this reason, we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
However, a surrogate loss is no good on its own; one needs a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\subsection{Property elicitation}\label{subsec:properties}
In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested report'' given $p$.
For intuition, one can conceptualize $p = D_x$ for some given input $x$.
Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
\begin{definition}[Property, elicits, level set]
	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to reports.
	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
	\begin{equation}
	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R}L(u;p)
	\end{equation}
	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which reporting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
\end{definition}

@@

While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal reports for $\Gamma$ must be linked back to \emph{all} optimal reports for $\gamma$.
Instead, we lighten this restriction to say that any optimal report for $\Gamma$ must be linked to \emph{an} optimal report for $\gamma$, and must be done deterministically.

@@

\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.  Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, we show that Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.

@@

\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.  E.g. embedding is actually a special case of indirect elicitation.  You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.  But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.  Try to spell it out carefully, but briefly :-).  If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}
\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
However, it is an open problem to understand the tightness of this hierarchy.

@@

\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
\raf{Should be in section 3}

@@

We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and report $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

@@

  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions.}
  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
  % Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
  % the next \hat Fs used to be F's
  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
  implying $\codim(\hat F) \geq \codim(F)$.

>>>>

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
\jessie{Alright, I tried...}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}\jessiet{Phew; feel free to delete this thread now.}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) provides a necessary condition for
\raft{Not a characterization!}\jessiet{right.... whoops.}
the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.

@@

\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.

Because the paper focuses heavily on conditional distributions over $\Y$ given some $x \in X$, we abstract away $x$ with the following notation.
The probability simplex over $\Y$ is $\simplex$.
For $p \in \simplex$, let $\supp(p)$ be the support of $p$.
For a distribution $p \in \simplex$, we denote the expected target loss for prediction $r$ to be $\E_{Y \sim p} \ell(r, Y) := \ell(r; p)$.
Similarly, $\E_{Y \sim p} L(u, Y) := L(u ; p)$.
We call the excess loss over the optimal the \emph{regret} of a loss $L(u; p)$; that is, $R_L(u,p) := L(u;p) - \inf_{u^*} L(u^*; p)$.

@@

\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We want to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this... probably needs to be pared down.}
Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

@@

\raf{Same general comment on style, etc, as intro.  See if you can get the point across in fewer words.}\jessie{Took a pass on this as well.}
For discrete prediction problems, we often start with a target loss $\ell$ in mind: for classification, 0-1 loss comes to mind; for high-confidence classification, a variation of 0-1 loss that allows a constant, moderate penalty for abstaining can be used.
%\raft{``Borda'', and anyway ML folks probably won't know what you mean}
However, optimizing over a target loss is often a computationally hard problem.
This is why we use surrogate losses, but desire consistency to guarantee the surrogate ``corresponds'' to the original loss, or property we want to predict, as is more common in the the continuous estimation setting.
A surrogate is no good on its own;we also need a link function to map from the surrogate prediction space back to the \emph{correct} prediction in the original prediction space.
This notion of a correct surrogate is typically captured by the notion of \emph{consistency}, introduced formally in Definitions~\ref{def:consistent-ell} and~\ref{def:consistent-prop}.
Related, and sometimes equivalent, is \emph{calibration}, which was the primary tool to study consistency until~\cite{agarwal2015consistent} introduced the use of property elicitation to study consistency in certain contexts.

@@

\subsection{Property elicitation}\label{subsec:properties}
In Section~\ref{sec:consis-implies-indir} we show that indirect property elicitation is also a necessary condition for constructing a consistent surrogate loss.
Informally, a property is a function mapping a probability distribution $p$ over the outcome set $\Y$ to the ``suggested prediction'' given $p$.
For intuition, one can conceptualize $p = D_x$ for some given input $x$.
Take the function  $\Gamma: \simplex \to 2^\R \setminus \emptyset$ to be denoted $\Gamma:\simplex \toto \R$.
\begin{definition}[Property, elicits, level set]
	A \emph{property} is a (possibly set-valued) function $\Gamma : \simplex \toto \R$ mapping distributions to predictions.
	A loss $L : \R \times \Y \to \reals_+$ \emph{elicits} the property $\Gamma$ if,
	\begin{equation}
	\forall p \in \simplex, \;\; \Gamma(p) = \argmin_{u \in \R}L(u;p)
	\end{equation}
	Moreover, we call a \emph{level set} $\Gamma_r := \{p \in \simplex : r \in \Gamma(p)\}$ to be the set of distributions for which predicting $u$ minimizes the expected loss of the loss eliciting $\Gamma$.
\end{definition}

@@

While there are a few possible definitions of indirect elicitation, this one is the most applicable for our setting because when we consider set-valued properties, we do not have that \emph{all} optimal predictions for $\Gamma$ must be linked back to \emph{all} optimal predictions for $\gamma$.
Instead, we lighten this restriction to say that any optimal prediction for $\Gamma$ must be linked to \emph{an} optimal prediction for $\gamma$, and must be done deterministically.

@@

\raf{I'd start off by motivating / explaining what all of these notions are trying to do, and perhaps fold in some related work discussion from above.  Like ``Various works have tried to quantify how difficult a learning problem is by determining the minimum dimension of a consistent surrogate loss...'' or similar.}\jessie{Attempted with the previous paragraph.}
\cite{ramaswamy2016convex} introduce a notion of \emph{convex calibration dimension} for discrete losses similar to elicitation complexity mentioned above; we discuss this further in Section~\ref{sec:finite-calib}.
Their convex calibration dimension results yield consistent surrogates for discrete prediction problems such as hierarchical classification from~\cite{ramaswamy2015hierarchical} and classification with an abstain option studied by~\cite{ramaswamy2018consistent}.
However, we show that Theorem~\ref{thm:cvx-flats} can be used to derive their convex calibration bounds, and even derive tighter bounds on convex calibration dimension in some instances.

@@

\raf{It makes sense to discuss this here, but be a bit more precise with how they relate.  E.g. embedding is actually a special case of indirect elicitation.  You can say we show that calibration and indirect elic are equivalent for polyhedral losses, in the sense that if a polyhedral loss indirectly elicits a discrete loss, it is calibrated wrt that loss.  But we don't know exactly how ``convex elic complex'', ``embedding dimension'', ``polyhedral calibration dimension'', and ccdim relate.  Try to spell it out carefully, but briefly :-).  If too long, we can punt some of the discussion, especially the last bit on open questions, to the discussion.}\jessie{Attempted....}
\cite{finocchiaro2019embedding} additionally presents the notion of a surrogate loss \emph{embedding} a discrete loss, which is a special case of indirect elicitation.
They show that for polyhedral (piecewise linear and convex) losses, calibration and indirect elicitation are equivalent.
Moreover,~\cite{finocchiaro2020embedding} introduces the notion of \emph{embedding dimension}, which is a lower bound on both convex elicitation complexity of discrete properties and convex calibration dimension of discrete losses.
Since embedding is a special case of indirect elicitation, there is a hierarchy of complexity notions in which embedding dimension $\preceq$ convex elicitation complexity and embedding dimension $\preceq$  ``polyhedral calibration dimension'' $\preceq$ convex calibration dimension.
However, it is an open problem to understand the tightness of this hierarchy.

@@

\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
\raf{Should be in section 3}\jessie{In the first paragraph of \S 3}

@@

We regain the bounds provided by~\cite[Theorem 16]{ramaswamy2016convex}, but have to do a little bit of groundwork to translate from our Theorem~\ref{thm:cvx-flats} and their result, restated in Corollary~\ref{cor:fsd-bound}.
First, in Lemma~\ref{lem:feas-sub-is-a-flat}, we show that, for a fixed $p$ and prediction $r$ so that $r \in \gamma(p)$, the feasible subspace $\Sc_{\gamma_r}(p)$ is a flat satisfying the requirements of Theorem~\ref{thm:cvx-flats}.
Therefore, we have the dimension of $\Sc_{\gamma_r}(p)$ being upper bounded by $d$, at least for $p \in \relint{\simplex}$. 
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat in $\affhull(\simplex)$ containing $p$ such that $F \cap \simplex \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
  Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$.
  Now consider $v \in F - p$.
  Since $p \in \relint{\simplex}$, there is an open ball of radius $\epsilon$ in the affine hull of $\simplex$ so that for all $q \in B(p, \epsilon)$, we have $q \in \simplex$.
  In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \simplex$.
  Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
  Since level sets of elicitable properties are convex (\cite{lambert2009eliciting}) this is true for all $\alpha' \leq \alpha$.
  Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%  First, if $p+v \in \gamma_r$ and $p -v \in \gamma_r$, then we have $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = 1$ as level sets of elicitable properties are convex by~\cite{lambert2009eliciting}.
%  If either $p + v$ or $p - v \not \in \gamma_r$, it must be because the term is out of the simplex by definition of $F$.
%  
%  However, if both $p + \alpha^+ v$ and $p - \alpha^- v \in \simplex$ for some $\alpha^\pm \in (0,1)$, then $v \in \Sc_{\gamma_r}(p)$ with $\epsilon_0 = \min(\alpha^+, \alpha^-)$.
%  As $p \in \relint{\simplex}$, there is always such an $\epsilon_0$; if there were not, then we would observe $v \not \in F - p$.
%  Therefore, we have $v \in F - p \implies v \in \Sc_{\gamma_r}(p)$, so $(F - p) \subseteq \Sc_{\gamma_r}(p)$.
\end{proof}

@@

  By Theorem~\ref{thm:cvx-flats}, as $\hat L$ elicits $\hat\Gamma$ and indirectly elicits $\Gamma$, there is a level set $\hat\Gamma_{\hat r}$ and flat $\hat F\subseteq\affhull(\simplex)$ containing $p$ such that $\codim(\hat F) \leq k$ and $S := \hat F \cap \simplex \subseteq \hat\Gamma_{\hat r} \subseteq \Gamma_r$.
  \raft{This last statement does follow from the proof of our main theorem, but it takes a second to realize that we show the chain of inclusions. \jessie{Tried to clarify in that proof}}
  Let $F = \affhull(\Gamma_r)$ and recall $\codim(F)=d$.
  % Let $F' = \hat F \cap \affhull(\simplex)$, and observe the following: $p\in F'\cap\relint\simplex$, $F' \subseteq \affhull(\simplex)$, $S=F'\cap\simplex\subseteq\Gamma_r$, and $\codim(F') \leq k+1$.
  % the next \hat Fs used to be F's
  As $p\in \hat F\cap\relint\simplex$, Lemma~\ref{lem:affhull-relint} gives $\affhull(S) = \affhull(\hat F\cap \simplex) = \hat F$.
  Now as $S \subseteq \Gamma_r$, we also have $\hat F = \affhull(S) \subseteq \affhull(\Gamma_r) = F$,
  implying $\codim(\hat F) \geq \codim(F)$.
